onsetsync demo

### 2022-12-23 README.Rmd
updated link
updated readme

@@

```{r fig2,warning=FALSE,fig.width=7, fig.asp=.7}
inst <- c('Clave','Bass','Guitar','Tres') # Define instruments 
dn <- sync_execute_pairs(CSS_Song2,inst,0,1,'SD')
fig2 <- plot_by_pair(dn)  # plot
print(fig2)  
```

@@

```{r paired1}
set.seed(1234) # set random seed
N <- 200 # Let's select 200 onsets
Bootstrap <- 1000
d1 <- sync_sample_paired(CSS_Song2,'Clave','Bass',N,Bootstrap,'SD',TRUE)
print(paste('Mean asynchrony of',round(mean(d1$asynch*1000),1),
    'ms & standard deviation of',round(sd(d1$asynch*1000),1),'ms'))
```

@@

For more examples, see [Get started](docs/articles/onsetsync.html).

>>>>

For documentation, see [ Quick Guide](https://tuomaseerola.github.io/onsetsync/articles/onsetsync.html).

@@

```{r fig2,warning=FALSE,fig.width=7, fig.asp=.7}
inst <- c('Clave','Bass','Guitar','Tres')              # Define instruments 
dn <- sync_execute_pairs(CSS_Song2, inst, beat = 'SD') # Calculate ansychr.
fig2 <- plot_by_pair(dn)                               # Plot
print(fig2)  
```

@@

```{r paired1}
set.seed(1234) # set random seed
N <- 200 # Let's select 200 onsets
Bootstrap <- 100 # Let's bootstrap this 100 times
d1 <- sync_sample_paired(df=CSS_Song2,
                         instr1 = 'Clave',
                         instr2 = 'Bass',
                         n = N,
                         bootn = Bootstrap,
                         beat = 'SD')
dplyr::summarise(data.frame(d1), N=n(), M = mean(asynch*1000), SD = sd(asynch*1000))
```

@@

For more examples, see [Get started](https://tuomaseerola.github.io/onsetsync/articles/onsetsync.html).
